Do We Judge Children's Books by Their Covers? 

### 2024-12-03 paper/paper.qmd
Update paper title

---
title: "Children's book paper"
subtitle: "Subtitle"
author: 
  - David Qi
thanks: "Code and data are available at: https://https://github.com/UTDQi/children_book_review"
date: today
date-format: long
abstract: ""
format: pdf
number-sections: true
toc: true
bibliography: references.bib
---

@@

Children's books, as a unique genre, present distinct dynamics in the realm of user-generated ratings and recommendation systems. Unlike adult literature, children rarely contribute directly to ratings or reviews. Instead, parents, educators, and caregivers typically provide feedback. Since they are not direct reader of the book, their rating may subject to greater bias from first impression.

@@

[results]

>>>>

---
title: "Do We Judge Children's Books by Their Covers? "
subtitle: "Exploring Title, Exclamation Marks, and Reviewer Bias"
author: 
  - David Qi
thanks: "Code and data are available at: https://https://github.com/UTDQi/children_book_review"
date: today
date-format: long
abstract: ""
format: pdf
number-sections: true
toc: true
bibliography: references.bib
---

@@

However, children's books, as a unique genre, present distinct dynamics in the realm of user-generated ratings and recommendation systems. Unlike adult literature, children rarely contribute directly to ratings or reviews. Instead, parents, educators, and caregivers typically provide feedback. Which have made is difficult to create recommendation systems [@judgecover]. And since many reviewer are not direct reader of the book, we hypothysize their rating may subject to greater bias from first impression.

@@

As a result, we found that one may explain 7.94% variation in the data by title alone. This fact along with the significant F statistics of linear regression model, have reflected the small but clearly present influence of first impression on book ratings. We have develop theories, by looking at our model output and relating to relevant literature, that as a sign of excitement and celebration, exclamation marks can provide a positive first impression and improve rating. We also note the influence of number of pages and review to rating ratio on average rating, and considered possible causation.
